On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-06-22 documents/paper.tex
???

It is important to remember to normalize the gaussian pulse, or else numerical noise will be introduced.

@@

@@

>>>>

It is important to remember to normalize the gaussian pulse, or else numerical noise will be introduced. The precise magnitude is not important - [Luebbers 1992/1991] use 100v, others use 1v, etc.

@@

A step impulse (1 first timestep, 0 otherwise) can also be used, though the performance is almost unusable worse.

@@

The impedance of a microstrip antenna varies with position on its plane. Probe feeds that couple a microstrip to a specific point are often used.
